Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-12 paper/latex/paper.tex
more edits from last commit

For a slight modification on this setting, we no longer attempted to identify which instrument was present if it was not one of the two instruments whose pitch class was being identified. Instead, the classifier would simply identify that an instrument that was not one of the two was present. Since this is a simpler problem, it lead to increased accuracies. Flute and Violin went from 30.2\% to 38.8\%, Oboe and French Horn from 27.3\% to 39.9\%, and Trombone and Bass Tuba from 2.2\% to 3.5\%. \textit{(I think we should maybe put a table of this data instead of listing it all out)} Random Forest performed significantly worse for this setting. Flute and Violin had an accuracy of 9.8\% and Oboe and French Horn was 17.5\%. For this reason, we stopped testing with Random Forest and continued with SVM only.

>>>>

For a slight modification on this setting, we no longer attempted to identify which instrument was present if it was not one of the two instruments whose pitch class was being identified. Instead, the classifier would simply identify that an instrument that was not one of the two was present. Since this is a simpler problem, it lead to increased accuracies. The accuracies from this experiment are outlined in Table 1. Since Random Forest performed worse than SVM is every experiment, we stopped testing with Random Forest and used SVM from that point on.
